---
title: "genproc: Shiny Proof of Concept"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{genproc: Shiny Proof of Concept}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = FALSE
)
library(genprocpoc)
```
  
# Overview

`genproc` provides a minimal Shiny interface to run batch processes driven by a mask (a data frame where each row defines one execution case).

The application is structured into four steps:

1. Upload a mask
2. Define a function
3. Configure and launch the process
4. Inspect logs

The goal of this vignette is to demonstrate how to use the Shiny application through a reproducible demo workflow.

# Demo and how to use

To get started, generate a ready-to-use demo framework: 

```{r}
create_demo_framework("path/to/demo")
```

This creates the following elements within `"path/to/demo"`, which we'll refer as `"./"` from now on: 

- a mask file (`"./mask/mask.csv"`)
- a demo function and argument mapping (`"./func/func_and_args_mapping.R"`)
- input datasets (R built-in ones, `"./r_built_in_datasets/"`)
- an empty output directory (`"./out/"`)

Then, launch the application with: 

```{r}
run_app()
```

The interface contains four sections: 

- 1 - Mask
- 2 - Function
- 3 - Execution
- 4 - Results

## Step 1 - Upload the mask

Upload the file at `"./mask/mask.csv"`. 
  
The application then validates the file format, loads it as a data frame and displays a preview.  
  
Each row of the mask represents one execution case. 

## Step 2 - Define function (and its arguments mapping with the mask names)

Open this file: `"./func/func_and_args_mapping.R"`. 
  
Copy the function part into the corresponding area in the app and click *Validate function*. 
  
Similarly, get the arguments mapping part in the app and click *Validate mapping*.   
  
The application ensures that mapping names match function arguments and mapping values match mask column names. 
  
## Step 3 - Configure and run  

- Set a process label  
- Select a directory for upcoming logs (e.g. at `"./out/"`)
- Click *Run*  
  
The application will adapt the function to the mask, wrap execution with error handling and execute the tasks in parallel. For your information, the number of workers is set by default to `parallel::detectCores() / 2` (half of your available cores).  
  
## Step 4 - Retrieve logs

Click *Get logs*

The application reads the log file named `"[proc_label].rds"` within the previously defined logs directory, and displays it in a table. Its structure is basically that of the mask + a `success` flag and an `error message` if applicable. 
 
  
